### 2017-08-31 docs/latex/annotated.tex
Documentation update

\section{Lista de componentes}
Lista de classes, estruturas, uniões e interfaces com uma breve descrição\-:\begin{DoxyCompactList}
\item\contentsline{section}{\hyperlink{structinstruction_line}{instruction\-Line} }{\pageref{structinstruction_line}}{}
\item\contentsline{section}{\hyperlink{structtoken}{token} }{\pageref{structtoken}}{}
\end{DoxyCompactList}