### 2017-12-05 docs/latex/annotated.tex
docs

\section{Lista de componentes}
Lista de classes, estruturas, uniões e interfaces com uma breve descrição\-:\begin{DoxyCompactList}
\item\contentsline{section}{\hyperlink{structdata_unit}{data\-Unit} }{\pageref{structdata_unit}}{}
\item\contentsline{section}{\hyperlink{structinstruction}{instruction} }{\pageref{structinstruction}}{}
\item\contentsline{section}{\hyperlink{structinstruction_line}{instruction\-Line} }{\pageref{structinstruction_line}}{}
\item\contentsline{section}{\hyperlink{structlabel}{label} }{\pageref{structlabel}}{}
\item\contentsline{section}{\hyperlink{structlabel_dir}{label\-Dir} }{\pageref{structlabel_dir}}{}
\item\contentsline{section}{\hyperlink{structlabel_macro}{label\-Macro} }{\pageref{structlabel_macro}}{}
\item\contentsline{section}{\hyperlink{structmen__chunk}{men\-\_\-chunk} }{\pageref{structmen__chunk}}{}
\item\contentsline{section}{\hyperlink{structmini__processor}{mini\-\_\-processor} }{\pageref{structmini__processor}}{}
\item\contentsline{section}{\hyperlink{structsymbol}{symbol} }{\pageref{structsymbol}}{}
\item\contentsline{section}{\hyperlink{structtoken}{token} }{\pageref{structtoken}}{}
\end{DoxyCompactList}