### 2017-12-05 docs/latex/files.tex

\section{Lista de ficheiros}
Lista de todos os ficheiros com uma breve descrição\-:\begin{DoxyCompactList}
\item\contentsline{section}{\hyperlink{assembler_8cpp}{assembler.\-cpp} }{\pageref{assembler_8cpp}}{}
\item\contentsline{section}{\hyperlink{assembler_8h}{assembler.\-h} }{\pageref{assembler_8h}}{}
\item\contentsline{section}{\hyperlink{languagedefinition_8h}{languagedefinition.\-h} }{\pageref{languagedefinition_8h}}{}
\item\contentsline{section}{\hyperlink{lexer_8cpp}{lexer.\-cpp} }{\pageref{lexer_8cpp}}{}
\item\contentsline{section}{\hyperlink{lexer_8h}{lexer.\-h} }{\pageref{lexer_8h}}{}
\item\contentsline{section}{\hyperlink{linker_8cpp}{linker.\-cpp} }{\pageref{linker_8cpp}}{}
\item\contentsline{section}{\hyperlink{loader_8cpp}{loader.\-cpp} }{\pageref{loader_8cpp}}{}
\item\contentsline{section}{\hyperlink{macroeval_8cpp}{macroeval.\-cpp} }{\pageref{macroeval_8cpp}}{}
\item\contentsline{section}{\hyperlink{macroeval_8h}{macroeval.\-h} }{\pageref{macroeval_8h}}{}
\item\contentsline{section}{\hyperlink{main_8cpp}{main.\-cpp} }{\pageref{main_8cpp}}{}
\item\contentsline{section}{\hyperlink{msgs__pt_8h}{msgs\-\_\-pt.\-h} }{\pageref{msgs__pt_8h}}{}
\item\contentsline{section}{\hyperlink{parser_8cpp}{parser.\-cpp} }{\pageref{parser_8cpp}}{}
\item\contentsline{section}{\hyperlink{parser_8h}{parser.\-h} }{\pageref{parser_8h}}{}
\item\contentsline{section}{\hyperlink{preprocessor_8cpp}{preprocessor.\-cpp} }{\pageref{preprocessor_8cpp}}{}
\item\contentsline{section}{\hyperlink{preprocessor_8h}{preprocessor.\-h} }{\pageref{preprocessor_8h}}{}
\item\contentsline{section}{\hyperlink{simulator_8cpp}{simulator.\-cpp} }{\pageref{simulator_8cpp}}{}
\item\contentsline{section}{\hyperlink{simulator_8h}{simulator.\-h} }{\pageref{simulator_8h}}{}
\item\contentsline{section}{\hyperlink{test__simulator_8cpp}{test\-\_\-simulator.\-cpp} }{\pageref{test__simulator_8cpp}}{}
\end{DoxyCompactList}